Twists of supersymmetric gauge theories

### 2019-10-29 paper.tex
paper

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$):
\[
(\phi, \Bar{\phi}, \psi_\pm) \in 
\]
The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
The field content for the BRST fields in the gauge sector is:
\[
(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
\]

For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
\[
(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
\]
We have written down the full BV action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm BV, gauge}$.

@@

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
& \pm g^2 \int (\phi \Bar{\phi}) * (\phi \Bar{\phi}) 
\end{align*}
\brian{add terms involving antifields}

@@

Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$ by:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda)\> + \<\lambda^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda^*) Q_- + (Q_-, \lambda^*)Q_+)\right\> .
\end{align*}

These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we state in the following proposition.
The result appears in \cite{SWchar}, and we do not repeat the proof here.

@@

\begin{proof}
First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
It is clear that
\[
\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 ,
\]
so we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.

Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.

@@

We start by computing the variation of $\psi_+ + \psi_-$:
\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = Fierz / 3 \psi \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

Next, we move on to the gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
\end{align*}

The matter fields decompose as
\begin{align*}
\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
\psi_- & \mapsto \beta_0 + \beta_{2,0} \in \Omega^{0,0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) .
\end{align*}

There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
\begin{itemize}
\item The twisted theory is a shifted cotangent theory in the BV formalism. 
This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
\end{itemize}

The first symmetry we exploit is translation invariance. 
There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
Let $\fg$ and $R$ be a Lie algebra together with a representation.
Define the following graded Lie algebra
\[
\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
\]
One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.

\begin{prop}
The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
\[
\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
\]
\end{prop}

>>>>

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
The field content for the BRST fields in the gauge sector is:
\[
(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
\]

For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
\[
(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
\]

Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.

@@

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
&\brian{where does this term come from \pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R}
\end{align*}
\brian{add terms involving antifields}

@@

The action of supersymmetry on the gauge sector is encoded by the functionals:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
\end{align*}

These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.

%The result appears in \cite{SWchar}, and we do not repeat the proof here.

@@

\begin{proof}
Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.

First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
\[
\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
\]
So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.

@@

We start by computing the variation of $\psi_+ + \psi_-$:
\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
For concreteness, we will fix a nonzero supercharge of negative chirality $$Q = Q_- \in S_-$$ to twist by. 
Such supercharges are minimal (i.e. have two dimensional image).  
They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

\begin{itemize}
\item[(1)] 
We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
\end{align*}
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
\end{align*}

The matter fields decompose as
\begin{align*}
\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
\end{align*}
and their antifields:
\begin{align*}
\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
\end{align*}

\item[(2)] Next, we study the linear differential in the twisted theory. 
At the linear level, the matter and gauge sectors completely decouple. 
For the matter sector, the linear differential is:
\[
\xymatrix{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
& \Omega^0(\CC^2; R)_{\gamma_0} \ar[r] & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
}
\]
For the gauge sector, the linear differential is:
\[
\xymatrix{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
\Omega^0(\CC^2; \fg)_{A_0} \ar[r] & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
}
\]
\end{itemize}

%There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
%\begin{itemize}
%\item The twisted theory is a shifted cotangent theory in the BV formalism. 
%This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
%\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
%\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
%\end{itemize}
%
%The first symmetry we exploit is translation invariance. 
%There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
%Let $\fg$ and $R$ be a Lie algebra together with a representation.
%Define the following graded Lie algebra
%\[
%\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
%\]
%One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
%Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$. 
%
%
%\begin{prop}
%The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
%\[
%\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
%\]
%\end{prop}
